---
title: "Midtermproject1021"
author: "Qi Huang"
date: "10/21/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE,warning=FALSE}
pacman::p_load(ggplot2,readr,leaflet,dplyr,data.table,xlsx,readxl,plotly,countrycode,tm,tidyverse,tidytext,wordcloud,grid,gridExtra,mosaic,faraway)
```

## R Markdown

This project is trying to investigate if investment in different industry segments would impact on the amount of CO2 emission. Varibales being choosed are CO2 emissions total, CO2 emissions per capita, CO2 emissions per GDP, investment in energy, investment in telecommunication, investment in transportation, investment in water.

1. Get Data
```{r,warning=FALSE}
data<-read_xls("climate_change_download_0.xls",sheet = 1,col_types = "guess",na = "..")
summary(data)
```

2. Data Cleaning
```{r,warning=FALSE,}
mydata<-dplyr::filter(data,`Series code` =="IE.PPI.ENGY.CD" |`Series code` == "IE.PPI.TELE.CD"|`Series code` =="IE.PPI.TRAN.CD" |`Series code` =="IE.PPI.WATR.CD"|`Series code` =="EN.ATM.CO2E.PC"|`Series code` =="EN.ATM.CO2E.PP.GD.KD"|`Series code` =="EN.ATM.CO2E.KT")
names(mydata)[1]<-"countrycode"
names(mydata)[2]<-"countryname"
names(mydata)[3]<-"seriescode"
names(mydata)[4]<-"seriesname"
mydata<-mydata %>% as.data.frame() %>% melt(measure.var=7:28)
names(mydata)[7]<-"year"
summary(mydata)
names(mydata)
spreadtest<-tidyr::unite(mydata,"series",c("seriesname","seriescode"),sep="",remove=TRUE,na.rm=FALSE)
spreadtest$SCALE=NULL
spreadtest$Decimals=NULL
spreadtest<-tidyr::spread(spreadtest,series,value)
names(spreadtest)[4]<-"CO2percapita"
names(spreadtest)[5]<-"CO2perGDP"
names(spreadtest)[6]<-"CO2total"
names(spreadtest)[7]<-"investenergy"
names(spreadtest)[8]<-"investtelecom"
names(spreadtest)[9]<-"investtransport"
names(spreadtest)[10]<-"investwater"
selected<-filter(spreadtest,countrycode=="ARG"|countrycode=="BRA"|countrycode=="ARG"|countrycode=="CHL"|countrycode=="CHN"|countrycode=="COL"|countrycode=="IDN"|countrycode=="IND"|
                   countrycode=="MEX"|countrycode=="MYS"|countrycode=="PER"|countrycode=="PHL"|countrycode=="RUS"|countrycode=="THA")
```

3. Data Visualization
3.1. CO2 emission for all selected countries
```{r,warning=FALSE}
table1<-xtabs(~CO2total+countryname,data=spreadtest)
table1<-aggregate(CO2total~countryname,rm.na=TRUE,data=spreadtest,FUN = sum)
table2<-xtabs(~CO2percapita+countryname,data=spreadtest)
table2<-aggregate(CO2percapita~countryname,rm.na=TRUE,data=spreadtest,FUN=sum)
table3<-xtabs(~CO2perGDP+countryname,data=spreadtest)
table3<-aggregate(CO2perGDP~countryname,rm.na=TRUE,data=spreadtest,FUN = sum)
#total CO2 emission between year 1990 and year 2011 for all countries 
ggplot(spreadtest,aes(x=countryname,y=CO2total,color=year))+geom_point()+geom_smooth()
#CO2 percapita between year 1990 and year 2011 for all countries
ggplot(spreadtest,aes(x=countryname,y=CO2percapita,color=year))+geom_point()+geom_smooth()
#CO2 perGDP between year 1990 and year 2011 for all countries
ggplot(selected,aes(x=countryname,y=CO2perGDP,color=year))+geom_point()+geom_smooth()
#the overall trend of total CO2 emission for all coutries considered as a population
ggplot(spreadtest,aes(x=year,y=CO2total))+geom_point()+geom_smooth()
#the overall trend of CO2 emission per capita for all coutries considered as a population
ggplot(spreadtest,aes(x=year,y=CO2percapita))+geom_point()+geom_smooth()
#the overall trend of CO2 emission per GDP for selected countries that have continious investments on different industries
ggplot(selected,aes(x=as.numeric(as.character(year)),y=CO2perGDP,color=countryname))+geom_point()+geom_smooth()
#the CO2 emission per GDP between year 1990 and year 2011 for selected countries
plot_ly(selected,x=~as.numeric(as.character(year)),y=~CO2perGDP,type='scatter',mode='lines')
#the CO2 total emission between year 1990 and year 2011 for selected countries
plot_ly(selected,x=~as.numeric(as.character(year)),y=~CO2total,type='scatter',mode='lines')
#the CO2 emission per capita between year 1990 and year 2011 for selected countries
plot_ly(selected,x=~as.numeric(as.character(year)),y=~CO2percapita,type='scatter',mode='lines')
```

3.2. Top emission from country (CO2 emission per GDP)
```{r,warning=FALSE}
clean<-na.omit(spreadtest)
topemission<-arrange(table3,CO2perGDP)
ggplot(head(topemission,n=10),aes(countryname,CO2perGDP,fill=countryname,label=paste(CO2perGDP)))+geom_bar(sta='identity',color='black')+
  coord_flip()+theme_bw()+theme(legend.position = 'none')+geom_text(aes(y=1),hjust=0,vjust=0.5,size=4)+
  labs(title='Top countries with highest CO2 emission per GDP')
```

3.3 Comparing Investment in Different Segments with CO2 Emission for Each Selected Country
```{r,warning=FALSE}
ARG<-filter(selected,countrycode=="ARG")
plot_ly(ARG,x=~ARG$year,y=~ARG$CO2percapita,name="CO2percapita",type='scatter',mode='lines') %>% 
  add_trace(y=~scale(ARG$investenergy),name='energy',mode="lines+markers") %>% 
  add_trace(y=~scale(ARG$investtelecom),name='telecom',mode='lines+markers') %>% 
  add_trace(y=~scale(ARG$investtransport),name='transport',mode='lines+markers')
```

3.4 Use the 13 Countries as a Sample to Test if Investment in Different Segments would Impact the Amount of CO2 Emission
```{r,warning=FALSE}
sample<-na.omit(selected[3:10])
trace_0<-aggregate(sample$CO2percapita,by=list(year=sample$year),FUN=sum)
trace_1<-aggregate(sample$investenergy,by=list(year=sample$year),FUN=sum)
trace_2<-aggregate(sample$investtelecom,by=list(year=sample$year),FUN=sum)
trace_3<-aggregate(sample$investtransport,by=list(year=sample$year),FUN=sum)
plot_ly(sample,x=~trace_0$year,y=~trace_0$x,name="CO2percapita",type='scatter',mode='lines') %>% 
  add_trace(y=~scale(trace_1$x),name='energy',mode='lines+markers') %>% 
  add_trace(y=~scale(trace_2$x),name='telecom',mode='lines+markers') %>% 
  add_trace(y=~scale(trace_3$x),name='transport',mode='lines+markers')
cor.test(sample$CO2percapita,sample$investenergy)
cor.test(sample$CO2percapita,sample$investtelecom)
cor.test(sample$CO2percapita,sample$investtransport)
```

Based on both the EDA and the correlation test, investment in difference segments does not have significant impact on CO2 emission.
Limitations would be:
1. The 13 countries, as a sample, could be not representative regarding the whole world. 
2. Simple linear coefficient model shoule be validated using residual check. 